{How do we copy and paste?\\The semantic drift of quotations in blogspace}

### 2014-12-30 brains-protocol.tex
4.1 comment on heatmap

The other features --- Age of acquisition, Number of phonemes, Clustering coefficient and Number of synonyms --- do not seem to exhibit any particularly significant effect on susceptibility.
For each of these features, it is indeed possible to draw a constant line which always remains within the respective confidence intervals.  If these variables have an effect, it is by no means as strong as it is for Word frequency.  This is remarkably clear for Clustering coefficient and Number of synonyms, where susceptibility values remain within quite small intervals (respectively [0.09-0.13] and [0.11-0.15]).  We may notice a somewhat marked effect for the highest values of Age of acquisition and Number of phonemes, where the mean susceptibility is almost twice higher than for the rest (respectively 0.19 vs 0.13, and 0.21 vs 0.12).  Keeping in mind the poor statistical significance of this effect, we could still suggest that the longest and late-learned words are more susceptible.  To examine further this phenomenon, we plotted the two-dimensional map of joint susceptibility values for these two features (heatmap at the bottom right of Fig.~\ref{fig:feature-susceptibilities}).
\TB{We see that \todo{}}.
\TB{This class of words corresponds to \todo{} [\TB{highly specialized words? domain-specific? a hard limit on too complicated words?}]}
%Age of acquisition and Number of phonemes delineate two categories of words: both features have little to no significant effect on susceptibility for low- to mid-valued words, but very high-valued words behave differently and tend to be more substituted (clearly for high Number of phonemes, and only as a tendency for high Age of acquisition).
%These high-valued words also have low occurrence frequencies, which corresponds to the slope change in the frequency curve between extreme low frequency words and mid- to high-frequency words. \rk{check this with a plot of freq vs. clustering and freq vs. AoA, or simply plot of frequency for the high-valued words for AoA and CC.}

>>>>

The other features --- Age of acquisition, Number of phonemes, Clustering coefficient and Number of synonyms --- do not seem to exhibit any particularly significant effect on susceptibility.
For each of these features, it is indeed possible to draw a constant line which always remains within the respective confidence intervals.  If these variables have an effect, it is by no means as strong as it is for Word frequency.  This is remarkably clear for Clustering coefficient and Number of synonyms, where susceptibility values remain within quite small intervals (respectively [0.09-0.13] and [0.11-0.15]).  We may notice a somewhat marked effect for the highest values of Age of acquisition and Number of phonemes, where the mean susceptibility is almost twice higher than for the rest (respectively 0.19 vs 0.13, and 0.21 vs 0.12).  Keeping in mind the poor statistical significance of this effect, we could still suggest that the longest and late-learned words are more susceptible.  To examine further this phenomenon, we plotted the two-dimensional map of joint susceptibility values for these two features (heatmap at the bottom right of Fig.~\ref{fig:feature-susceptibilities}).
\TB{We see that outlier values (the two darkest cells) are both due to cells where the number of items is only slightly above the significance threshold (11 items, while we decided to cut at 10). If we focus on cells based on at least several dozens of words, values range from 0.11 to 0.22 with little obvious regularity, making it hard to draw any conclusion as regards the direction of an effect and confirming the fact that the slight late increases observed for Age of acquisition and Number of phonemes were rather non-significant.}
%\TB{This class of words corresponds to \todo{} [\TB{highly specialized words? domain-specific? a hard limit on too complicated words?}]}
%Age of acquisition and Number of phonemes delineate two categories of words: both features have little to no significant effect on susceptibility for low- to mid-valued words, but very high-valued words behave differently and tend to be more substituted (clearly for high Number of phonemes, and only as a tendency for high Age of acquisition).
%These high-valued words also have low occurrence frequencies, which corresponds to the slope change in the frequency curve between extreme low frequency words and mid- to high-frequency words. \rk{check this with a plot of freq vs. clustering and freq vs. AoA, or simply plot of frequency for the high-valued words for AoA and CC.}
